Analysis of the olfactory data

### 2017-05-11 R/zinbwave_olfactory.Rmd
clusterExp html

### Three dimensions
```{r zinb}
print(system.time(zinb_3 <- zinbFit(core, ncores = 3, K = 3)))
```

@@

### Five dimensions

@@

### Ten dimensions

@@

@@

```{r}
print(system.time(zinb_3_qc <- zinbFit(core, ncores = 3, K = 3, X = mod)))
```

@@

K = 5
```{r}
print(system.time(zinb_5_qc <- zinbFit(core, ncores = 3, K = 5, X = mod)))
```

@@

K = 10
```{r}
print(system.time(zinb_10_qc <- zinbFit(core, ncores = 3, K = 10, X = mod)))
```

@@

@@

@@

K = 5
```{r}
print(system.time(zinb_5_batch <- zinbFit(core, ncores = 3, K = 5, X = mod)))
```

@@

K = 10
```{r}
print(system.time(zinb_10_batch <- zinbFit(core, ncores = 3, K = 10, X = mod)))
```

@@

@@

```{r}
print(system.time(zinb_3_qc_batch <- zinbFit(core, ncores = 3, K = 3, X = mod)))
```

@@

K = 5
```{r}
print(system.time(zinb_5_qc_batch <- zinbFit(core, ncores = 3, K = 5, X = mod)))
```

@@

K = 10
```{r}
print(system.time(zinb_10_qc_batch <- zinbFit(core, ncores = 3, K = 10, X = mod)))
```

>>>>

We are going to look at different parameters for ZINB

- K (3, 5, and 10),
- X (intercept only, accounting for QC, accounting for batch, accounting for QC and batch).

### No cell covariate

Using only intercepts in X and V.

#### Three dimensions
```{r zinb}
print(system.time(zinb_3 <- zinbFit(core, ncores = 3, K = 3)))
```

@@

#### Five dimensions

@@

#### Ten dimensions

@@

X has an intercept and 5 additional columns with the first five PC on qc measures.

@@

#### Three dimensions
```{r}
print(system.time(zinb_3_qc <- zinbFit(core, ncores = 3, K = 3, X = mod)))
```

@@

#### Five dimensions
```{r}
print(system.time(zinb_5_qc <- zinbFit(core, ncores = 3, K = 5, X = mod)))
```

@@

#### Ten dimensions
```{r}
print(system.time(zinb_10_qc <- zinbFit(core, ncores = 3, K = 10, X = mod)))
```

@@

X has an intercept and columns for the batchs.

@@

#### Three dimensions

@@

#### Five dimensions
```{r}
print(system.time(zinb_5_batch <- zinbFit(core, ncores = 3, K = 5, X = mod)))
```

@@

#### Ten dimensions
```{r}
print(system.time(zinb_10_batch <- zinbFit(core, ncores = 3, K = 10, X = mod)))
```

@@

X has an intercept, columns for the batches, and columns with the first five PC on QC measures.

@@

#### Three dimensions
```{r}
print(system.time(zinb_3_qc_batch <- zinbFit(core, ncores = 3, K = 3, X = mod)))
```

@@

#### Five dimensions
```{r}
print(system.time(zinb_5_qc_batch <- zinbFit(core, ncores = 3, K = 5, X = mod)))
```

@@

#### Ten dimensions
```{r}
print(system.time(zinb_10_qc_batch <- zinbFit(core, ncores = 3, K = 10, X = mod)))
```
